\papertitle

### 2012-10-11 manuscript.tex

@@

We determined the backwards reachable set of initial states for successful
window traversal both geometrically and in simulation. The results are shown
in Figure~\ref{fig:feasible_set}. The initial conditions that we chose are
spatially gridded in the camera viewing region at 0.05 meter increments and an
initial angular position perpendicular to the window plane. The geometrically
infeasible region is indicated in blue and was computed using the minimum
turning radius and simple geometry. Both the regions in red and blue indicate
the infeasible region determined in simulation. We simulated the turning model
described in Section~\ref{sec:flight_control}, with a PID controller steering
the system to the center of the window as the input. The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.
\\
To verify the feasible region experimentally, we conducted trials at initial
distances in X meter increments from the window along the edges of the image
frame of the camera. We started each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figure~\ref{fig:flight_paths}.
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO ryan
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.

>>>>

To judge the performance of our system described in the previous sections, we
determined the feasible set of initial conditions that resulted in successful
window traversal. We then conducted experiments to calculate the success rate
both within the feasible region and on the edges of the feasible region. The
following sections detail how we calculated the feasible and infeasible
regions using system identification and present the results of our
experimental trials.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths_feasible.pdf}
\caption{Plot of camera field of view and experimental trials within the feasible region.}
\label{fig:flight_paths_feasible}
\end{figure}

We determined the backwards reachable set of initial states for successful
window traversal both geometrically and in simulation. The results are shown
in Figure~\ref{fig:feasible_set}. The initial conditions that we chose are
spatially gridded in the camera viewing region at 0.05 meter increments and an
initial angular position perpendicular to the window plane. The geometrically
infeasible region is indicated in blue and was computed using the minimum
turning radius and simple geometry. Both the regions in red and blue indicate
the infeasible region determined in simulation. We simulated the turning model
described in Section~\ref{sec:flight_control}, with a PID controller steering
the system to the center of the window as the input. The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.
\\
To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from the window along the
edges of the image frame of the camera. We started each trial with an initial
heading perpendicular to the window plane. The results of the experiments are
shown in Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 79\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region (Figure~\ref{flight_paths}), the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending on the PID
tuning and the distance from the camera.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO ryan
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.
